Road traffic sound level estimation from realistic urban sound mixtures by Non-negative Matrix Factorization

### 2018-07-31 revision/responseToreviewers.tex

\documentclass[10pt]{article}

\title{Reply to reviewer concerning submission APAC$\_$2018$\_$311 'Road traffic sound level estimation from realistic urban sound mixtures by Non-negative Matrix Factorization' in Applied Acoustics.}

\begin{document}

\maketitle

As a preamble, we would like to thank the editor and the reviewer for the comments and suggestions. Following these comments, we made several changes to the article, which are summarized here. The next sections list our answers to the reviewer’s comments, with references to the revised manuscript (page, column, and paragraph) where appropriate.

\section{Answers to Reviewer 1}

An interesting approach to estimate the sound level of road traffic in an urban sound environment composed of a mixture of sound sources is presented in the reviewed paper.

The work is well planned and structured. It has an adequate length and the results are interesting.

I only have some minor indications that I think they can improve a little bit this paper.

\begin{enumerate}
\item The use of the letter beta should be clarified because its use in expressions (5, 8a, 8b and 8c) and in lines 104-105, seems not to be the same that its use in expressions (4a, 4b y 4c) or, for example, in tables 3 and 4.\\
$\rightarrow$ Done, The $\beta$ value is the same, the choice of the $\beta$-divergence in the equation 4 influes the way the expressions 5 and 8 are then updated. This has been precised . 'Thus, the choice of the $\beta$-divergence in the equation affects how the matrix $\mathbf{H}$ is updated.' (section 2.1).

\item In relation with table 4, it may be appropriate that it includes some more complete representation or table of results, for the reader interested in analyzing in more detail the effects that the different variables analyzed may have on errors. For example, one in which, varying one of the variables analyzed, the others remain constant.

$\rightarrow$ We add a part dedicated to this where the influence of the number of element on $\mathbf{W}$ and the temporal window $w_t$ influence the NMF behavior.

\item References: The bibliographic revision is good, but maybe, some references can be improved.

For example, reference (3), because it is a congress, not a peer reviewed paper. Only as an example, you can considerer the references: https://doi.org/10.1016/j.apacoust.2010.06.010 and https://doi.org/10.1016/j.scitotenv.2011.10.018 .

In line 67, it is indicated that “Many works…” but only two references are included. Author may considerer others, for example: 
http://dx.doi.org/10.1016/j.apacoust.2016.05.020 and https://doi.org/10.2478/v10168-012-0054-z

At the end of the lines 30-31, it is possible that some general references are needed. For example, 
https://doi.org/10.3813/AAA.918456 and http://dx.doi.org/10.1016/j.apacoust.2016.04.018.\\
$\rightarrow$ Done, some references have been add to the different locations indicated.

\item Moreover, there are references that just have been submitted to publication. \\
$\rightarrow$ Done for one reference, the other is still in revision.

\end{enumerate}

\end{document}

### 2018-07-31 revision/articleNmfTrafficSimScene2018_v2.tex
Responses to reviewers

In response to the growing demand from urban dwellers for a better environment, noise mapping has been recommended as a tool to tackle noise pollution. The enactment of the European Directive 2002/EC/49 makes such maps mandatory to cities over 100 000 inhabitants. Those maps play an important informative role, establishing the distribution of the sound levels all over the cities as well as the estimation of the number of city dwellers exposed to high sound level ($>$ 55 dB(A)) \cite{nugent2014noise}. Road traffic concentrates particular attention as it is the main urban source of noise annoyance. Road traffic noise maps are typically built from data collection that consist of traffic data collected on the main roads (flow rates, mean speeds and heavy vehicle ratio) and urban geographic data (building heights and location, topology, ground surfaces \dots). Follows sound emission and sound propagation computational techniques, resulting in the production of the two indicators equivalent A-weighted sound levels, $L_{DEN}$ (\textit{Day-Evening-Night}) and $L_N$ (\textit{Night}) \cite{kephalopoulos2012common}. This procedure also enables drawing up action plans to reduce the noise exposure. Despite their unanimously recognized interest, noise maps suffer from some limitations. The computing cost required to produce noise maps at the city scale calls simplifications of the numerical tools and the simulation models that both generate uncertainties \cite{van_leeuwen_noise_2015}. Data collection is itself also a vector of uncertainty. Moreover, the produced aggregated indicators do not model the sound levels evolution due to the traffic variations throughout the day.

Noise measurements are thus increasingly used in addition to simulation to describe urban noise environments. Several measurement set-ups have been proposed in the last years, including  mobile measurements with high quality microphones \cite{manvell2004sadmam, can2014measurement}, participative sensing through dedicated smartphone applications \cite{picaut:halshs-01565214, ventura2017evaluation}, or the development of fixed-sensor networks. In this latter case, the sensor networks can be based either on high-quality sensors as in \cite{mietlicki2012innovative, maijala2018environmental}, or low-cost sensors as in the DYNAMAP project \cite{dynamap_2016} or the CENSE project \cite{picaut2017characterization}. The costs and benefits of each protocol are discussed. Mobile and participatory measures increase spatial coverage at low cost, but lack temporal representativeness. Fixed networks are very reliable for measuring sound levels temporal variations, but allow only a small spatial coverage of the network. In addition, the low-cost sensors enable a wider deployment, but at the cost of increased uncertainties, the most extreme example being smartphone applications.

@@

Many works have dealt with the detection \cite{luitel2016sound} or the recognition \cite{defreville_automatic_2006} of sound events in environmental sound scenes. In these cases, a two-step scheme is followed where audio samples are described with a set of features (Mel Frequency Cepstral Coefficient, MPEG-7 descriptors \dots) and classified with the help of a classifier (Gaussian Mixtures Models, Artificial Neural Network \dots) \cite{chu2008environmental, cowling_comparison_2003}. The classifier is learnt from a learning database and is next applied on a test database to validate the algorithms.
Dedicated to the traffic, in \cite{socoro_anomalous_2017}, an Anomalous Event Detection, based on MFCC features, is proposed with the specific aim to improve the traffic sound estimation. It is based on the detection of unwanted sound events in order to discard them.

@@

with $\gamma(\beta) = \frac{1}{2-\beta},$ for $\beta < 1$, $ \gamma(\beta) = 1$, for $\beta \in \left[1,2\right]$ and $\gamma(\beta) = \frac{1}{\beta-1}$ for $\beta > 2$. The $A\otimes B$ and $A/B$ operators represent the Hadamard product and ratio.

@@

\begin{figure*}[t]
\centering
\includegraphics[width=0.8\linewidth]{figures/realistic_urban_sound_scene_design.pdf}
\caption{Bloc diagram of the design of the evaluation corpus}
\label{fig:transcription}
\end{figure*}

>>>>

In response to the growing demand from urban dwellers for a better environment, noise mapping has been recommended as a tool to tackle noise pollution. The enactment of the European Directive 2002/EC/49 makes such maps mandatory to cities over 100 000 inhabitants. Those maps play an important informative role, establishing the distribution of the sound levels all over the cities as well as the estimation of the number of city dwellers exposed to high sound level ($>$ 55 dB(A)) \cite{nugent2014noise}. Road traffic concentrates particular attention as it is the main urban source of noise annoyance. Road traffic noise maps are typically built from data collection that consist of traffic data collected on the main roads (flow rates, mean speeds and heavy vehicle ratio) and urban geographic data (building heights and location, topology, ground surfaces \dots). Follows sound emission and sound propagation computational techniques, resulting in the production of the two indicators equivalent A-weighted sound levels, $L_{DEN}$ (\textit{Day-Evening-Night}) and $L_N$ (\textit{Night}) \cite{kephalopoulos2012common}. This procedure also enables drawing up action plans to reduce the noise exposure. Despite their unanimously recognized interest, noise maps suffer from some limitations. The computing cost required to produce noise maps at the city scale calls simplifications of the numerical tools and the simulation models that both generate uncertainties \cite{arana2011precision,van_leeuwen_noise_2015}. Data collection is itself also a vector of uncertainty. Moreover, the produced aggregated indicators do not model the sound levels evolution due to the traffic variations throughout the day.

Noise measurements are thus increasingly used in addition to simulation to describe urban noise environments \cite{gozalo2016study,zannin2013characterization,can_exploring_2012}. Several measurement set-ups have been proposed in the last years, including  mobile measurements with high quality microphones \cite{manvell2004sadmam, can2014measurement}, participative sensing through dedicated smartphone applications \cite{picaut:halshs-01565214, ventura2017evaluation}, or the development of fixed-sensor networks. In this latter case, the sensor networks can be based either on high-quality sensors as in \cite{mietlicki2012innovative, maijala2018environmental}, or low-cost sensors as in the DYNAMAP project \cite{dynamap_2016} or the CENSE project \cite{picaut2017characterization}. The costs and benefits of each protocol are discussed. Mobile and participatory measures increase spatial coverage at low cost, but lack temporal representativeness. Fixed networks are very reliable for measuring sound levels temporal variations, but allow only a small spatial coverage of the network. In addition, the low-cost sensors enable a wider deployment, but at the cost of increased uncertainties, the most extreme example being smartphone applications.

@@

Many works have dealt with the classification \cite{valero2012hierarchical,shen_environmental_2012}, the detection \cite{luitel2016sound,mesaros2015sound} or the recognition \cite{defreville_automatic_2006,parascandolo_recurrent_2016} of urban sound events. In these cases, a two-step scheme is followed where audio samples are described with a set of features (Mel Frequency Cepstral Coefficient, MPEG-7 descriptors \dots) and classified with the help of a classifier (Gaussian Mixtures Models, Artificial Neural Network \dots) \cite{chu2008environmental, cowling_comparison_2003}. The classifier is learnt from a learning database and is next applied on a test database to validate the algorithms.
Dedicated to the traffic, in \cite{socoro_anomalous_2017}, an Anomalous Event Detection, based on MFCC features, is proposed with the specific aim to improve the traffic sound estimation. It is based on the detection of unwanted sound events in order to discard them.

@@

with $\gamma(\beta) = \frac{1}{2-\beta},$ for $\beta < 1$, $ \gamma(\beta) = 1$, for $\beta \in \left[1,2\right]$ and $\gamma(\beta) = \frac{1}{\beta-1}$ for $\beta > 2$. Thus, the choice of the $\beta$-divergence in the equation \ref{eq:divBetaGenerale} affects how the matrix $\mathbf{H}$ is updated. The $A\otimes B$ and $A/B$ operators represent the Hadamard product and ratio.

@@

\begin{figure*}[t]
\centering
\includegraphics[width=0.8\linewidth]{./figures/realistic_urban_sound_scene_design.pdf}
\caption{Bloc diagram of the design of the evaluation corpus}
\label{fig:transcription}
\end{figure*}
